Comparative Evaluation of Spark and Flink Stream Processing

### 2017-03-03 paper/paper.tex
updated the spark implementaion of statistcs computation

\subsubsection{Statistics Computation per Trajectory}
In the first stream processing workload, we construct stream of trajectories by considering  the aircraft's positions (i.e., ADS-B messages) that belong to the same aircraft as trajectory. Moreover, we continuously compute and aggregate statistics for each arriving position in a trajectory . As example of computed statistics quantities speed mean, mean of location coordinates, min and max altitude, etc. In this workload, we  cover the parallel receiving of input data stream, statefull aggregation over the input data stream, and preserving the correct order of the stream's records.
The implementation details of this workload in Spark and Flink are presented in the following: 
\begin{itemize}
\item {\bf{Implementation in Spark }}

\par The Spark Streaming implementation of trajectory statistics computation read the Kafka stream using \texttt{KafkaUtils.createDirectStream} that creates \texttt{DStream} instance, in order to scale up and have parallel Kafka stream receivers, a multiple instances of \texttt{DStream} are created and combined together using \texttt{union} operation. The output stream of the \texttt{union} is processed using \texttt{mapToPair}, to map each position message to tuple of aircraft ID and position message. Then, the irrelevant tuples are filtered based on the position message type using  a \texttt{filter} transformation. Afterward, the tuple with same aircraft ID are groped together to construct trajectories (tuples of Id and list of positions), by applying the \texttt{groupByKey} operation. Since streaming model of Spark is micro-batch based and stateless, \texttt{updateStateByKey} operation is must be used to manage the state between the batches. In context of this workload, the statistics computation is preformed within the custom \texttt{updateStateByKey} function, which uses the last position of trajectory from previous batch to aggregate and compute statistics values to each trajectory's position in the new arriving batch.  The list of new positions must be sorted to preserve the correct order, since the tuples after \texttt{groupByKey} operation are shuffled across the cluster's  nodes.

>>>>

\subsubsection{Statistics Computation per Trajectory}
In the first stream processing workload, we construct a stream of trajectories by considering  the position messages (i.e., ADS-B messages) that belong to the same aircraft as trajectory. Moreover, we continuously compute and aggregate statistics for each new position in a trajectory . As example of computed statistics quantities speed mean, mean of location coordinates, min and max altitude, etc. In this workload, we cover the parallel receiving of input data stream, statefull aggregation over the input data stream, and preserving the correct order of the stream's records.
The implementation details of this workload in Spark and Flink are presented in the following: 
\begin{itemize}
\item {\bf{Implementation in Spark }}

\par The Spark Streaming implementation of trajectory statistics computation reads the Kafka stream using \texttt{KafkaUtils.createDirectStream} that creates \texttt{DStream} that represents the stream of position messages, in order to scale up and have parallel Kafka stream receivers, a multiple instances of \texttt{DStream} must be created and combined together using the \texttt{union} operation. The output stream of the \texttt{union} is further processed using \texttt{mapToPair}, to map each position message to tuple of aircraft ID and position message. Then, the irrelevant tuples are filtered based on the position message type using  a \texttt{filter} transformation. Afterward, the tuples that share the same aircraft ID are groped together to construct the stream of trajectories (tuples of Id and list of positions), by applying the \texttt{groupByKey} operation. Since the processing  model of Spark Streaming is micro-batch based and stateless, \texttt{updateStateByKey} operation must be used to maintain the state of the trajectories stream. In the context of this workload, the state is the aggregated statistics of trajectory, so the statistics computation is preformed within the custom \texttt{updateStateByKey} function that continuously applied for every batch.
 The state update function uses the last position of trajectory from previous batch to aggregate and compute statistics quantities to each trajectory's position in the new data batch, and the new positions list is kept as the new state for the trajectory. Inside the state update function, the new positions must be sorted to preserve the correct order, since the tuples after \texttt{groupByKey} operation are shuffled across the cluster's  nodes and sent to the state update function.
